Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-16 Background.tex
Rewriting background

%!TEX root = disclosure_game.tex
%Rewrite all of this, ditch the alcohol stuff altogether. Any really key can be woven in elsewhere (discussion)
\section{Background}

@@

This section presents a brief overview of literature focusing on the theoretical underpinning of the modelling
approach, with particular reference to statistical decision theory.

\subsection{Games, Signals, and Decisions}
\label{sub:games_signals}

\subsubsection{Signalling Games}

Game theory generally deals with strategic decision making in the
unusual circumstance of complete information, that is, every player
has at least complete knowledge of all possible outcomes, who their
opponents are, and so forth. Arguably more generally applicable is
the incomplete information scenario, where players lack information
about the rules of play in some fashion. \citet{Harsanyi1967} proposed
a method for effectively transforming such games into games of complete
information by treating the possible variations on the rules as subgames.
To determine which subgame is to be played, an additional player -
nature - is introduced to make the first move, where nature conducts
a lottery according to some probability distribution. If it is assumed
that the underlying probability distribution is known to all players,
the game is then one of complete information.

Perhaps the best known example of Bayesian games, are the signalling
games codified by \citet{Kreps1987}, after initially being framed
by \citet{Spence1973} in the context of employment markets. The general
form of such a game is that one player holds information known only
to them, on the basis of which they send a signal to the other player(s),
which the other player(s) then act upon. Much of the interest in signalling
games turns on what conditions are necessary for honest signalling
to be a Nash equilibrium, or in the context of evolutionary game theory,
an \ac{ESS} .

One approach to this requires that signalling is a costly exercise,
as proposed by \citet{Grafen1990} in examining biological signals
(for example, the eye-catching but unwieldy peacock tail). \citeauthor{Grafen1990}
demonstrated that an earlier suggestion by \citet{Zahavi1975}, who
proposed that such signals were in effect a handicap demonstrating
fitness, would lead to an \ac{ESS} because of the costly nature of
the signalling. This solution is also noted by \citet{Spence1973},
who showed that a separating equilibrium exists%
\footnote{In fact, an infinite number of them.%
} contingent on signals being more costly for some types.

Costly signalling has been applied to explain a variety of apparently
contradictory behaviours, for example \citet{Godfray1991} in the
context of offspring soliciting food from parents, where the key question
is why a behaviour with potentially very high costs (namely, being
eaten) would be preferred to a less risky method. In a social context,
costly signalling has been proposed as an explanation for religion
in human societies. \citet{Sosis2003} developed a model of religious
ritual as an exercise in costly signalling, showing that higher costs
to engagement in rituals for skeptics maintains the stability of religious
groups and the presumed benefits that membership confers. \citet{Henrich2009}
extended this idea, and developed an evolutionary model combining
cultural transmission with costly signalling in a population, finding
that for even modest costs the system moved towards universal belief.
\citet{Wildman2011} subsequently extended the model, to address the
fact that both stable equilibria are binary states, finding that the
incorporation of group differentiation allowed subgroups to persist.

Signalling games have also been extended to provide models of other
observed human behaviour, for example \citet{Austen-Smith2005} attempted
to explain the observed poor academic attainment of some social groups
by positing a multiple audience signalling game. They found that the
introduction of a secondary signalling game with a peer audience,
alongside the prototypical \citeauthor{Spence1973} model introduced
a pooling equilibrium. Subsequent empirical work by \citet{Jr2010}
has provided some support for this idea. Along similar lines, \citet{Feltovich2002}
examine an observed failure by high quality types to signal as would
be anticipated, introducing the concept of countersignaling in scenarios
where there is noisy leakage of type information. They found that
where there is added noisy type information available, separating
equilibriums exist where high quality senders signal either as low
quality, or not at all.

\subsubsection{Bayesian Decision Theory and Expected Utility}

Decision theory is the theory of rational decision making \citep{Peterson2009},
this contrasts with game theory which is concerned with strategic
decision making. In the broadest sense, the field can be divided into
two types of theories: normative, and descriptive. Normative theories
are those which attempt to give the rational answer to a decision
problem, descriptive or behavioural theories focus instead on characterising
the process of human decision making. In this instance, the particular
concern is with theories of decision making under uncertainty.

Underpinning almost all theories of decision making, and much of economic
theory in general is the concept of expected utility, originally proposed
by \citet{Bernoulli1954}. This casts decisions as choices between
lotteries or gambles, with differing payoffs and probabilities.

>>>>

%!TEX root = disclosure_game.tex
%Rewrite all of this, ditch the alcohol stuff altogether. Any really key can be woven in elsewhere (discussion)
\section{Previous Research}

@@

This section presents a brief overview of previous research, addressing in turn signalling games, normative decision theory, heuristic decision making, and descriptive decision theory.

\subsection{Signalling Games}

The preponderance of classical game theory focuses on strategic decision making, in scenarios where all players have complete information about all aspects of the game. An alternative, perhaps more common situation, is that players have incomplete information, i.e. their knowledge of the rules of play is in some way deficient. \citet{Harsanyi1967} introduced the concept of a Bayesian game, resolving the problems introduced by the incomplete information scenario by allowing the possible variations on the rules to be treated as subgames. This adds an additional player - nature, to the game, where nature takes the first move thereby deciding which subgame is played. Nature is assumed to make their move by lottery, and where the probability distribution governing the lottery is known to all players this permits the game to be formulated as one of complete information. Here, we are specifically interested in signalling games \citep{Kreps1987,Spence1973}, where one player holds some private information which may be communicated (or not) by means of a signal.

This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \ac{ESS}. \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g. peacock tail feathers), then honest signalling would constitute an \ac{ESS}. \citet{Spence1973} demonstrated similar results in a game of job market signalling, where signal cost was differentiated by type. Costly signalling has also been suggested as an explaination of behaviour that at first gasp appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal carries a risk of being eaten. Moving beyond animal behaviour, \citet{Sosis2003} considered the implications if ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.

Other work augments the signalling game model, for example \citet{Austen-Smith2005} adds a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subseqent empirical support for the idea from \citet{Jr2010}. On a similar tack, \citet{Feltovich2002} introduced additional noisy type information, finding that this effectively explained counterintuitive observed behaviour where actors with every right to boast of their quality faail to do so.

\subsection{Normative Decision Theory}

Where game theory addresses strategic decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.  Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem. An alternative view - descriptive, or behavioural decisin theory, holds that the focus should instead be on giving an account of human decision making, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}. Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context (section \ref{sub:heuristic_theories}).

The conceptual underpinning of all of these is the central idea of expected utility, originated by \citet{Bernoulli1954} and later formalised by \citet{Neumann1953}, which treats all decisions as gambles defined in terms of payoffs and probabilities.

\subsection{Heuristic Decision Making}\label{sub:heuristic_theories}

As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making.

\subsection{Descriptive Decision Theory}\label{sub:descriptive_theories}

While normative theories are concerned with how decisions should be made, descriptive theories instead focus on how decisions are made.
